Secure Composition \\ of Robust and Optimising Compilers

### 2024-09-19 csf2/main.tex
typo fix

$\Lscct$ extends $\Lms$ (\Cref{subsec:lms}) with a ,,constant-time mode''. 
The activation of the mode can be checked ($\obj{\lrddoit{x}{\expr}}$), changed ($\oobj{\lwrdoit{D}}$), and is stored in program states ($\obj{\Omega}$).
At the beginning of program execution of $\Lscct$ programs, the mode is turned off ($\obj{OFF}$).
If the mode is enabled (i.e., set to $\obj{ON}$), the intuition is that no secrets are leaked. 
This models the real-world\footnote{As present in Intel~\cite[p.80]{intel-refman} and ARM~\cite[p.~543]{arm-refman} processors.} data-independent timing mode as well as the result of compiling a program with FaCT~\cite{cauligi2019fact}.
For example, FaCT rewrite code that branches to use a constant-time selection primitive.
To not obfuscate our formalisation unnecessarily by duplicating syntax, we simply added the ,,constant-time mode'' to $\Lscct$.

>>>>

$\Lscct$ extends $\Lms$ (\Cref{subsec:lms}) with a ,,constant-time mode''. 
The activation of the mode can be checked ($\obj{\lrddoit{x}{\expr}}$), changed ($\obj{\lwrdoit{D}}$), and is stored in program states ($\obj{\Omega}$).
At the beginning of program execution of $\Lscct$ programs, the mode is turned off ($\obj{OFF}$).
If the mode is enabled (i.e., set to $\obj{ON}$), the intuition is that no secrets are leaked. 
This models the real-world\footnote{As present in Intel~\cite[p.80]{intel-refman} and ARM~\cite[p.~543]{arm-refman} processors.} data-independent timing mode as well as the result of compiling a program with FaCT~\cite{cauligi2019fact}.
For example, FaCT rewrite code that branches to use a constant-time selection primitive.
To not obfuscate our formalisation unnecessarily by duplicating syntax, we simply added the ,,constant-time mode'' to $\Lscct$.
